Team size and composition in home health care

### 2023-10-25 paper-presentation/paper-presentation.qmd
Minor

::: columns
::: {.column width="40%"}
*The buffer capacity required to handle demand variability decreases with scale, but the possible reduction becomes smaller as the scale increases.*

@@

*The complexity of the number of interactions for a team of size* [$M$]{style="color: red;"} is $O(M^2)$. By splitting the team into [$k$]{style="color: red;"} sub-teams, managed by one mediator, the number of interactions can be reduced by a factor [$k$]{style="color: red;"} as [$M$]{style="color: red;"} grows large.

>>>>

::: columns
::: {.column width="40%"}
*The buffer capacity required to handle demand variability decreases with scale, but marginal reductions decrease as scale increases.*

@@

*The complexity of the number of interactions for a team of size [$M$]{style="color: red;"} is $O(M^2)$. By splitting the team into [$k$]{style="color: red;"} sub-teams, managed by one mediator, the number of interactions can be reduced by a factor [$k$]{style="color: red;"} as [$M$]{style="color: red;"} grows large.*
